---
format: gfm
---

# Jass

The Jass package contains the tools to play a game of Jass with one or more AI players.

The `training` branch contains a deep learning model to recognize cards, allowing the user to deal a physical hand of cards to a mix of real and AI players. It will also contain deep learning models for AI players.

The `annotation` branch contains a shiny app for input and annotation of image data needed for training of the card recognition model. Source images will be linked here at some point.

Not all of the names and terminology I use is standard, but I've tried to stick to the official rules ([see this site](https://www.swisslos.ch/en/jass/informations/jass-rules/schieber-jass.html)).

## Installation

```{r install, eval=FALSE}
devtools::install_github('johnsonra/Jass')
```

## A sample game

For now, the AI players only know how to play a valid card. It is little better than playing with a ghost hand, but the parts are in place to start working on smarter AI models.

Let's start by initializing a game of Cross Jass (this is what I always heard it called, although it is also called Schieber Jass).

```{r setup}
#| include: false
if(!require(Jass))
  devtools::load_all()
```

```{r}
#| eval: false
# load package
library(Jass)
```

```{r initialize Cross Jass}
# set the random seed so we get the same cards each time
set.seed(2389756)

g <- new('Game') |>
  set_human(1) |>    # we'll play for player #1 all other players are AI by default
  deal()
```

Now, lets see what cards we have in our hand. By default the first player's cards are shown.

```{r initial hand}
cards(g)
```

Looks like Bells is a decent choice for trump (i.e. Schellen).

```{r pick trump}
trump(g) <- 'Bells'

# cards are reordered according to trump precedence
cards(g)
```

Before the first card is played, we can check for melds (Stock and Wys). Each player declares any sequences of three or more cards in the same suit, four-of-a-kind combinations, or a marriage (King + Ober in the trump suit). Only the team with the highest individual meld scores all of their combined meld points.

```{r meld}
meld_result <- meld(g)

# See what each player can declare
lapply(meld_result$player_melds, function(m) {
  if(length(m) == 0) return("No melds")
  sapply(m, function(x) paste(x$type, x$points, 'pts'))
})

# Which team scores, and how much?
meld_result$team_scores
```

We'll jump right in with the first trick.

```{r trick1a}
# play Ace of Bells
g <- play(g, 'BA')
```

Now it is on to the AI players.

```{r trick1b}
# player 2 (AI) (we'll set auto to FALSE to only play one card here)
g <- play(g, auto = FALSE)

# player 3 (AI)
g <- play(g, auto = FALSE)

# player 4 (AI)
g <- play(g, auto = FALSE)

# end of trick
status(g)
g <- next_trick(g)
status(g)
```

Now that we see the general flow, lets auto-play the first half of this trick.

```{r trick2a}
# play for players 3 and 4
g <- play(g, auto = TRUE)

# check status and play
status(g)
cards(g)
g <- play(g, 'SB')

# continue play
g <- play(g, auto = TRUE)
status(g)
```

This has taken us through the end of the second trick. Player 3 has won the second trick again and started the third trick. We'll just zoom ahead now.

```{r trick3plus}
cards(g)
g <- play(g, 'A7', auto = TRUE)

status(g)
cards(g)
g <- play(g, 'B7')

g <- next_trick(g)
g <- play(g, 'F8', auto = TRUE)

status(g)
cards(g)
g <- play(g, 'S6', auto = TRUE)

status(g)
cards(g)
g <- play(g, 'BB', auto = TRUE)

status(g)
cards(g)
g <- play(g, 'AB', auto = TRUE)

status(g)
cards(g)
g <- play(g, 'B9', auto = TRUE)

status(g)
```

Next, lets try a fully automated round.

```{r autoGame}
set.seed(923847)
g2 <- new('Game') |>
  deal()

# pick trump
trump(g2) <- pick_random_trump(g2, 2)

g2 <- play(g2, auto = TRUE)
status(g2)
```

Now let's try a game with Gemini.

```{r gemini}
set.seed(9238476)
g3 <- new('Game') |>
  set_human(1) |>    # we'll play for player #1 all other players are AI by default
  deal()

trump(g3) <- 'Flowers'

g3 <- play(g3, 'FO', auto = FALSE, rules = pick_card_gemini, state = g3)
g3 <- play(g3, auto = FALSE, rules = pick_card_gemini, state = g3)
g3 <- play(g3, auto = FALSE, rules = pick_card_gemini, state = g3)
g3 <- play(g3, auto = FALSE, rules = pick_card_gemini, state = g3)


g3_1 <- play(g3, auto = TRUE, rules = pick_card_gemini, state = g3)


trk <- g3@round@trick
h <- g3@round@hands[[4]]
state <- g3
```